---
title: "Alcohol vs Seat choice"
author: "Aubrey Garcia"
date: "summer 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```

# Introduction

Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in??

The data came from UCDavis in the year...


$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.

$H_A$: The average number drinks is different between at least two rows. 

# Methods
In the Davisdata set is a categorical variable, alcohol is numerical.

we are trying to predict alcohol~seat so we use the nunerical~cat helper


# Results


## Descriptive results

### Graphical summary

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
Now add in boxplot

```{r}
basicCN + geom_boxplot()
```

This boxplot shows that those who sat in the back consumed more alchol in comparison to those in the middle and front.

### Numerical Summary

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```


The numerical results show the mean of alcohol consumption was 8.5 for those in the back, much higher than those in the front with a mean of 1.8 and those is the middle with a 3.3 mean.


### Inferential Results

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The P-vaule is 0.000116 which less than .5, so with that said we reject the null hypothesis.

There is a difference in alcohol consumption based on where people sit.


## When significant follow up with TukeyHSD  

```{r}
plot(TukeyHSD(model1))
```


According to the TukeyHSD  test shwon above there is no statistical difference in alcohol consumption and where the person sits.

## Conclusions

The original questions was weather if the row of where someone sits, have 
difference between the alcohol consumed. According to graphical summary, the box plot shows that those who sat in the back consumed more alcohol in comparison to those in the middle and front. Furthermore, the numerical summary shows the mean of alcohol consumption was 8.5 for those in the back, much higher than those in the front with a mean of 1.8 and those is the middle with a 3.3 mean. Then the inferential results showed that The P-value is 0.000116 which less than .5, so with that said we reject the null hypothesis. The null hypothesis says that there is no difference between the average number of drinks imbibed between people conditioned on the row they sit in, however while we do reject the null hypothesis according to the TukeyHSD there is no statistical difference in alcohol consumption.