---
title: "Alcohol vs Seat choice"
author: "Aubrey Garcia"
date: "summer 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```

# Introduction

Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in??

The data came from UCDavis in the 1990's


$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.

$H_A$: The average number drinks is different between at least two rows. 

# Methods
In the Davisdata set is a categorical variable, alcohol is numerical.

we are trying to predict alcohol~seat so we use the nunerical~cat helper


# Results


## Descriptive results

### Graphical summary

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
Now add in boxplot

```{r}
basicCN + geom_boxplot()
```

This boxplot shows that those who sat in the back consumed more alchol in comparison to those in the middle and front.

### Numerical Summary

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```


The numerical results show the mean of alcohol consumption was 8.5 for those in the back, much higher than those in the front with a mean of 1.8 and those is the middle with a 3.3 mean.


### Inferential Results

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The P-vaule is 0.000116 which less than .05, so with that said we reject the null hypothesis.

There is a difference in alcohol consumption based on where people sit.


## When significant follow up with TukeyHSD  

```{r}
plot(TukeyHSD(model1))
```


According to the TukeyHSD  test shwon above there is no statistical difference in alcohol consumption and where the person sits.

## Conclusions



The original questions was weather if  there was a difference between the alcohol consumed between the row they choose to sit in? The P-value is 0.000116 which less than .05, so with that said we reject the null hypothesis. There is a difference in alcohol consumption based on where people sit. According to the TuekeyHSD test there is a difference in sits with  front-back, and middle-back which was about 7 ounces. In the middle-front seats there was 0 statistical difference on alcohol consumption. 
